Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-21 tex/v3/appendix.tex

\subsection{Proof of Lemma~\ref{lemma_bounds_on_marginals}}

The optimality condition for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
\begin{align}
\label{i-th-marginal-mu} 
{\mu}^{\text{sc}}_i  &= 
\begin{cases}
e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I_{\varepsilon,\kappa},\\
\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}
\end{cases}
=\begin{cases}
\kappa \mu_i, \text{ if  }i \in I_{\varepsilon,\kappa},\\
\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa},
\end{cases}
\end{align}
and 
\begin{align}
\label{i-th-marginal-nu} 
{\nu}^{\text{sc}}_j  &= 
\begin{cases}
e^{v^{\text{sc}}_j} \sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J_{\varepsilon,\kappa},\\
\varepsilon\kappa\sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J^\complement_{\varepsilon,\kappa}
\end{cases}
=\begin{cases}
\frac{\nu_j}{\kappa}, \text{ if  }j \in J_{\varepsilon,\kappa},\\
\varepsilon\kappa\sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J^\complement_{\varepsilon,\kappa}.
\end{cases}
\end{align}

Using inequality~\eqref{bound_on_v}, we obtain 
\begin{align*}
\norm{\mu^{\text{sc}}}_1 &= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
\end{align*}
Again by left-hand-side of inequaltiy~\eqref{bound_on_v}, we arrive at 
\begin{align*}
\norm{\mu^{\text{sc}}}_1 %&= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
%& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
& \overset{}{\geq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n -n_b) \Big(\frac{mm_b\varepsilon^2 K_{\min}^2 \min_{j\in J_{\varepsilon, \kappa}} \nu_j}{ (n-n_b)m\kappa \varepsilon^2 K_{\min} + n_b\kappa^2 \max_{i\in I_{\varepsilon,\kappa}}\mu_i }+ (m-m_b)\varepsilon^2K_{\min}\Big),
\end{align*}
which gives the claimed result.
Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.

@@

We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
The violations are computed through the following function: 
	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other. The next Lemma is from~\cite{khalilabid2018} (see Lemma 7 herein).
\begin{lemma}
\label{lem:pinsker}
For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}
\end{lemma}

@@

% &\leq  \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)

@@

&\leq (n-n_b)\bigg(\frac{m_b}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i}\mu_i)^2}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)

@@

d_\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\

@@

\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}

@@

Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.

>>>>

@@

We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
The violations are computed through the following function: 
\begin{equation*}
	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
\end{equation*}
Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other. The next Lemma is from~\cite{khalilabid2018} (see Lemma 7 herein).
\begin{lemma}
\label{lem:pinsker}
For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
\begin{align*}
\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}.
\end{align*}
\end{lemma}

The optimality conditions for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
\begin{align}
\label{i-th-marginal-mu} 
{\mu}^{\text{sc}}_i  &= 
\begin{cases}
e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I_{\varepsilon,\kappa},\\
\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}
\end{cases}
=\begin{cases}
\kappa \mu_i, \text{ if  }i \in I_{\varepsilon,\kappa},\\
\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa},
\end{cases}
\end{align}
and 
\begin{align}
\label{i-th-marginal-nu} 
{\nu}^{\text{sc}}_j  &= 
\begin{cases}
e^{v^{\text{sc}}_j} \sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J_{\varepsilon,\kappa},\\
\varepsilon\kappa\sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J^\complement_{\varepsilon,\kappa}
\end{cases}
=\begin{cases}
\frac{\nu_j}{\kappa}, \text{ if  }j \in J_{\varepsilon,\kappa},\\
\varepsilon\kappa\sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J^\complement_{\varepsilon,\kappa}.
\end{cases}
\end{align}

@@

@@

&\qquad \leq (n-n_b)\bigg(\frac{m_b}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
&\qquad \qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i}\mu_i)^2}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)

@@

d_\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b c_{\kappa}\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\

@@

\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq & n_bc_{\kappa}\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).

@@

Following the same lines as above, we also have
\norm{{\nu} -{\nu}^{\text{sc}}}^2_1 \leq & m_bc_{\frac 1\kappa}\max_{i} \mu_i + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{mK_{\min}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
&+ \max_{j} \nu_j\log\Big(\frac{(m-m_b+ 1)\max_{j} \nu_j}{n_b\kappa K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{m_b(\max_{j} \nu_j)^2}{nn_b\varepsilon^2\kappa^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).%\bigg\}^{1/2}
To get the closed forms~\eqref{marginal-error-mu} and~\eqref{marginal-error-nu}, we used the follwoing facts:
\begin{remark}
\label{rem:orders_of_epsilonappa}
 We have 
$\varepsilon = \bigO((mnK_{\min}^2)^{-1/4})$, $\kappa= \bigO(\sqrt{m/(nc_{\mu\nu}K_{\min})}),$ $\kappa^{-1} = \bigO(\sqrt{n/(mK_{\min}c_{\mu\nu}})$, $(\kappa/\varepsilon)^2 = \bigO( m^{3/2} / \sqrt{nK_{\min}}(c_{\mu\nu})^{3/2})$, and $(\varepsilon\kappa)^{-2} = \bigO(n^{3/2}/\sqrt{mK_{\min}}c^{3/2}_{\mu\nu}).$
\end{remark}

\subsection{Proof of Proposition~\ref{prop:objective-error}}

We first define $\widetilde{K}$ a rearrgement of $K$ with respect to the active sets $I_{\varepsilon,\kappa}$ and $J_{\varepsilon,\kappa}$as follows:
\widetilde{K} = 
\begin{bmatrix}
K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} & K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\\
K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &K_{(I^\complement_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}
\end{bmatrix}.
Setting $\dt{\mu} = (\mu_{I_{\varepsilon,\kappa}}^\top, \mu_{I^\complement_{\varepsilon,\kappa}}^\top)^\top$, $\dt{\nu} = (\nu_{J_{\varepsilon,\kappa}}^\top, \nu_{J^\complement_{\varepsilon,\kappa}}^\top)^\top$ and for each vectors $u \in \R^n$ and $v\in \R^m$ we set $\dt{u} =(u_{I_{\varepsilon,\kappa}}^\top, u_{I^\complement_{\varepsilon,\kappa}}^\top)^\top  \text{ and } \dt{v} =(v_{J_{\varepsilon,\kappa}}^\top, v_{J^\complement_{\varepsilon,\kappa}}^\top)^\top.$
We then have 
\Psi_{\varepsilon, \kappa} (u,v) = \mathbf 1_n^\top \widetilde{K}(\dt{u}, \dt{v}) \mathbf 1_m - \kappa \dt{\mu}^\top \dt{u} - \kappa^{-1} \dt{\nu}^\top \dt{v},
and 
\Psi_{} (u,v) = \mathbf 1_n^\top \widetilde{K}(\dt{u}, \dt{v}) \mathbf 1_m - \dt{\mu}^\top \dt{u} - \dt{\nu}^\top \dt{v},
where
  \widetilde{B}(\dt{u}, \dt{v}) = \Delta(e^{\dt{u}})\widetilde{K} \Delta(e^{\dt{v}}).
Let us consider the convex function
	(\hat u, \hat v) \mapsto \inr{\mathbf 1_n, \widetilde{B}(\dt{\hat u}^{\text{}} ,\dt{\hat v}^{\text{}})\mathbf 1_m} - \inr{\kappa\dt{\hat u}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa^{-1}\dt{\hat v}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}.
Gradient inequality of any convex function g at point $x_o$ reads as $g(x_o) \geq g(x) + \inr{\nabla g(x), x_o - x}, \text{ for all } x \in \textbf{dom}(g).$
Applying the latter fact to the above function at point ($u^{\star}, v^{\star})$ we obtain
\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} &- \inr{\kappa\dt{u}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
& - \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\kappa\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
- \inr{\kappa^{-1}\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)\\
&\qquad \qquad  \leq \inr{\dt{u}^{\text{sc}} - \dt{u}^\star, (1-\kappa) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+ \inr{\dt{v}^{\text{sc}} - \dt{v}^\star, (1-\kappa^{-1}) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}.
Moreover,
\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
&= \inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa\dt{u}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}}, \dt{v}^{\text{sc}})\mathbf 1_n^\top}\\
&\qquad - \big( 
\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
- \inr{\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)\\
&\qquad + \inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}.
Hence,
\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+& \big( \inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m} \\
&- \inr{\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
- \inr{\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)\\
& \qquad -\inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} -\inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}\\
& \leq \inr{\dt{u}^{\text{sc}} - \dt{u}^\star, (1-\kappa) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+ \inr{\dt{v}^{\text{sc}} - \dt{v}^\star, (1-\kappa^{-1}) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
&\qquad + \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\kappa\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
- \inr{\kappa^{-1}\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big).
Then,
\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
&\leq \inr{\dt{u}^{\text{sc}} - \dt{u}^\star, (1-\kappa) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+ \inr{\dt{v}^{\text{sc}} - \dt{v}^\star, (1-\kappa^{-1}) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
&\qquad + \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\kappa\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
- \inr{\kappa^{-1}\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)
\\
&\qquad + \inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}\\
&\qquad - \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
- \inr{\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top \mathbf 1_n} \big),
which yields 
\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
&\leq  \inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} +\inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}\\
&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}.
Applying Holder's inequality gives 
\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
&\leq \norm{\kappa \dt{u}^{\text{sc}} - \dt{u}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 + \norm{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1\\
&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
&\leq \norm{\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 + \norm{\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1\\
&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
Note that
\begin{cases}
\norm{\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty = \norm{{u}^{\text{sc}} - {u}^\star}_\infty,\\
\norm{\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty = \norm{{v}^{\text{sc}} - {v}^\star}_\infty,
\end{cases}
\text{ and }
\begin{cases}
\norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 = \norm{{B}({u}^{\text{sc}} ,{v}^{\text{sc}})\mathbf 1_m - {\mu}}_1 = \norm{\mu^{\text{sc}} - \mu}_1,\\
\norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1 = \norm{{B}({u}^{\text{sc}} ,{v}^{\text{sc}})^\top\mathbf 1_n - {\nu}}_1 = \norm{\nu^{\text{sc}} - \nu}_1.
\end{cases}
\begin{align}
\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) &
\leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty \norm{\nu^{\text{sc}} - \nu}_1\nonumber\\
&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\dt{\mu}^{\text{sc}}} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\dt{\nu}^{\text{sc}}}\nonumber\\
&\leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty\norm{\nu^{\text{sc}} - \nu}_1 \nonumber\\
&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\label{priori_bounds_induction}
\end{align}

\paragraph{Bounds of}$\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty $.

If $r \in I^\complement_{\varepsilon, \kappa}$ then 
|({u}^{\text{sc}})_{r} - {u}^\star_r| 
&= \bigg|\log\bigg(\frac{\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m \frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
& \overset{(\star)}{\leq} \bigg|\log\bigg(\max_{1\leq i \leq m} \frac{K_{rj}e^{v^\star_j}}{\frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
& \leq \big|\max_{1\leq j \leq m} (v_j^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})\big|\\
& \leq \norm{v^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})}_\infty \\
& \leq \norm{v^\star - {v}^{\text{sc}}}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}}).
where the inequality $(\star)$ comes from the fact that $\frac{\sum_{j=1}^na_j}{\sum_{j'=1}^nb_{j'}} \leq \max_{1\leq j \leq n} \frac{a_j}{b_j}, \forall a_j, b_j>0.$
Now, if $r \in I_{\varepsilon, \kappa}$, then  we have 
|({u}^{\text{sc}})_{r} - {u}^\star_r|
= \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}})_j}}\bigg)\bigg|
\leq \bigg|\log\bigg(\frac{\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}})_j}}\bigg)\bigg|
\overset{(\star)}{\leq}\norm{v^{\text{sc}} - v^\star}_\infty.
If $s \in J^\complement_{\varepsilon, \kappa}$ then 
|({v}^{\text{sc}})_{s} - {v}^\star_s| &= \bigg| \log(\varepsilon\kappa) - \log(\frac{\nu_s}{\sum_{i=1}^n K_{is}e^{u^\star_i}})\bigg|\\
& \leq \bigg|\log\bigg(\max_{1\leq i \leq n} \frac{K_{is}e^{u^\star_i}}{\frac{\nu_s}{n\kappa\varepsilon}}\bigg) \bigg|\\
& \overset{(\star)}{\leq} \big|\max_{1\leq i \leq n} (u_i^\star - \log(\frac{\nu_s}{n\kappa\varepsilon})\big|\\
& \leq \norm{u^\star - \log(\frac{\nu_s}{n\kappa\varepsilon})}_\infty \\
& \leq \norm{u^\star - u^{\text{sc}}}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}).
If $s \in J_{\varepsilon, \kappa}$ then 
|({v}^{\text{sc}})_{s} - {v}^\star_s| 
= \bigg|\log\bigg(\frac{\kappa\sum_{i=1}^m K_{ri}e^{u^\star_i}}{\sum_{i=1}^m K_{ri}e^{(u^{\text{sc}})_i}}\bigg)\bigg|
 \leq \bigg|\log\bigg(\frac{\kappa\sum_{i=1}^m K_{ri}e^{v^\star_j}}{\sum_{i=1}^m K_{ri}e^{(u^{\text{sc}})_i}}\bigg)\bigg|
\overset{(\star)}{\leq} \norm{u^{\text{sc}} - u^\star}_\infty.
Therefore, we obtain the followoing bound:
\begin{align}
\label{induction_uppers_bounds}
\max\{\norm{u^\star - u^{\text{sc}}}_\infty, \norm{v^\star - v^{\text{sc}}}_\infty\} %&\leq \max\{\norm{u^\star - u^{\text{sc}}_0}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}), \norm{v^\star - v^{\text{sc}}_0}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}})\}\nonumber\\
&\leq \max\Big\{\norm{u^\star}_\infty + \norm{u^{\text{sc}}}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}), \norm{v^\star}_\infty + \norm{v^{\text{sc}}}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}})\Big\}\nonumber\\
&\leq 2\Big(\norm{u^\star}_\infty + \norm{v^\star}_\infty +  \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}}\big)\Big).
\end{align}
%where we used $u^{\text{sc}}_0 = \mathbf 0_n$ and $v^{\text{sc}}_0 = \mathbf 0_m.$ 
Now, Lemma 3.2 in~\cite{lin2019} provides an upper bound for the $\ell_\infty$ of the optimal solution pair $(u^\star, v^\star)$ of problem~\eqref{sinkhorn-dual} as follows:
$\norm{u^\star}_\infty \leq R$ and $\norm{v^\star}_\infty\leq R,$ where 
\begin{align}
\label{R_constant}
